---
title: "San Mateo Resources"
output: html_document
---

# San Mateo County Food Resources map
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(httr)
library(googlesheets4)
```

## Fetch data from Zonehaven
The original map lives here: https://community.zonehaven.com/. We are going to make get requests to the Zonehaven API to filter for different types of locations.
```{r}
zonehaven_URL <- "https://cluster.alpha.zonehaven.com/geoserver/zonehaven/wfs"
```

```{r}
## These are the stk_type queries that the different buttons on the map issue.
# queries <- c(
#   medical = "('hospitals','urgent_care','testing_facilities','pharmacies','medical')",
#   social_services = "('social_services')",
#   food = "('food')",
#   parks_recreation = "('park_rec')",
#   pet_services = "('pet_services')",
#   home_auto = "('home_auto')",
#   financial_legal = "('financial_legal')",
#   other = "('other')"
# )

## Use this if you want all data
cql_filter <- str_interp("county_id=2")
## Use this if you want only certain stk_types
# cql_filter <- str_interp("county_id=2 and stk_type IN ${queries[['food']]}")

response <- GET(
  zonehaven_URL, 
  query = list(
    service = "wfs",
    version = "2.0.0",
    request = "GetFeature",
    typeName = "stk_view",
    outputFormat = "application/json",
    cql_filter = cql_filter
  )
)
```

## Convert JSON response to tibble
The response gives us a list of "Features", which each have a "properties" field, which is itself a list of key-value pairs about a location.
```{r}
body <- content(response, "parsed")

convert_properties_to_df <- function(.x) {
  properties <- .x$properties
  # Collapse bbox list of coordinates to string
  properties$bbox <- str_c(properties$bbox, collapse = ', ')
  
  map(properties, ~ . %||% NA_character_) %>% # Replace NULL with NA
    as_tibble()
}

df <- body$features %>% 
  map_dfr(convert_properties_to_df)
```

## Clean data
```{r}
cleaned_raw <- df %>% 
  mutate_if(is.character, list(~ na_if(., ""))) %>% 
  mutate_if(is.character, list(~ na_if(., "-"))) %>% 
  mutate_if(is.character, list(~ na_if(., "n.a."))) %>% 
  mutate_if(is.character, list(~ na_if(., "unknown"))) %>% 
  mutate_if(is.character, list(~ na_if(., "Not available"))) %>% 
  mutate_at(c("stk_city", "stk_address"), ~str_to_title(.))
```

## Export data (two options)

### Export to Google Sheets
```{r}
data <- cleaned_raw
sheet_name <- 'all raw'

doc <- gs4_find("San Mateo County Resources Map, raw data") %>% 
  gs4_get()

sheet_add(ss = doc, sheet = sheet_name)
sheet_write(data = data, ss = doc, sheet = sheet_name)
```

### Export to rds
```{r}
write_rds(cleaned_raw, path = str_interp('san_mateo_raw.rds'))
```