---
title: "combined_data_formatting"
author: "Anjali Katta"
date: "08/05/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(googlesheets4)
library(lubridate)
library(tidyverse)
gs4_auth()
```

# Load Data

### Google Sheets Keys

```{r}
SNAP_key <- "1GvXQYE8OXvE05xRPjywZze6PwDq8gCF5hkfqhMUgZAs"
school_meal_key <- "1fea1BSSAhbSB0HLsatDaD8wxmwsF7ezQjNvjRK-QJQI"
comm_resource_key <- "11tdkyX0kR8nRwMUktohdp2Wx1fGiMiHrlUP4i_8ctPM"
legal_resource_key <- "1FCInt7l15AeS-Kn_ITc8zZNZG-x2B5FvP3snKLGGmSs"
mega_map_key <- "1SOUonPM40Si4LrPoGrkUnujbmLBxCQe1SdxydH2dVI4"
farmers_market_key <- "112fZriUQH7CyoGEiIJt7kbYBJ44YD4vYXDWxuHVIJGI"
bob <- "12m356n5GBUaNi9BRSExin1_cf86KggqgAgtSCJ9x8JE"
dom_violence <- "13Lx_SHZ0WsUEDGapYJ0G5JTHijL-AjKHLD43iLhLDI0"
```

### Loading Sheets

# Domestic Violence
```{r}dnesday
dom_violence_db <- 
  read_sheet(
    skip = 1,
    dom_violence,
    col_types = "cccdcddddcddccccccccccddddddddcccccDccddd"
    ) %>% 
  mutate(address = location)
```

# Black owned businesses 
```{r}
bob_db <-
  read_sheet(bob, na ="NA") %>% 
  rename(
    web_link = website,
    days_hours = hours_gmaps,
    status = status_gmaps, 
    lat = lat_gmaps,
    lon = lng_gmaps,
    provider_name = name
  ) %>% 
  separate(address_gmaps, sep = "CA", into = c("address", "zip")) %>% 
  select(-phone, phone = phone_gmaps) %>% 
  mutate(
    status = if_else(str_detect(status, "OPERATIONAL"), 1, 0) %>% replace_na(0),
    notes = 
      if_else(!is.na(ig), paste("Instagram: ", ig, ".", sep = ""), "") %>% 
      if_else(!is.na(other), paste(., "Other info:",other ), .),
    zip = str_extract(zip, "\\d+") %>% as.numeric(),
    address = str_remove(address, location) %>% str_remove_all(., ","),
    in_store_pickup = if_else(str_detect(service, "Takeout"), 1, 0),
    delivery = if_else(str_detect(service, "Delivery"), 1, 0),
    catering = if_else(str_detect(service, "Catering"), 1, 0)
  )
```

# snap
```{r}
SNAP_data <- 
  read_sheet(
    SNAP_key, 
    skip = 5,
    col_types = "?????d????????????????D?????????"
  ) %>% 
  drop_na(type) %>% 
  mutate_at(
    vars(
      EBT_pay_phone, 
      EBT_pay_online, 
      delivery, 
      pay_at_pickup, 
      curbside_pickup)
    ,
    ~ if_else(str_detect(.,"\\w"), "1", "") %>% as.numeric()
  ) %>% 
  mutate(
    days_hours = str_replace_all(days_hours, "–", "-"),
    status = str_to_lower(status)
  ) %>% 
  filter(!str_detect(type, "Doesn't"))
```

school meal data
```{r}
school_meal_data <-
  read_sheet(
    school_meal_key, 
    sheet = "School Sites",
    skip = 1,
    col_types = "cccdddccddcdddccddccccccccccDDcccccc"
  ) %>% 
  mutate(
    open_hour = na_if(open_hour, "N/A"),
    close_hour = na_if(close_hour, "N/A"),
    days_of_week = na_if(days_of_week, "N/A"),
    phone = if_else(str_detect(phone, "www"), "", phone),
    status = 
      if_else(str_detect(status, "Open"), 1, 0)
  )
```

comm resource_data 
```{r}
comm_resource_data <- 
  read_sheet(
    comm_resource_key, 
    sheet = "Data",
    skip = 1,
    col_types = "cccdccdddddcddcccccccddddddddddddddddcccccDccdddddddddd??????"
  ) %>% 
  mutate(
    additional_hours = 0,
    additional_hours1 = 0,
    type = type %>% str_to_lower() %>% str_replace_all(" ", "_"),
    resource =  case_when(
      str_detect(type, "restaurant") ~ 'restaurant',
      str_detect(type, "farm") ~ 'grocery',
      type == "core_service_agency" ~ "core",
      type == "groceries" ~ "grocery",
      TRUE ~ type
    ),
    provider_addloc2 = provider_addloc,
    provider_addloc = 
      if_else(str_detect(type, "health"), provider_name, provider_addloc), ##switching the names for health
    provider_name = 
      if_else(str_detect(type, "health"), provider_addloc2, provider_name)
  ) %>% 
  select(-provider_addloc2) %>% 
  filter(!resource %in% c("legal", "housing", "immigration", "domestic_violence", "other"))
```

legal resource
```{r}
##CURRENTLY THE NOTES IS THE MAP INSTRUCTION COLUMN
legal_resource_data <-
  read_sheet(
    legal_resource_key, 
    sheet = "DATA PULL HERE", 
    skip = 1,
    col_types = "???????dd????????????????????D???"
  ) %>% 
  mutate(
    type = type %>% str_to_lower() %>% str_replace_all(" ", "_"),
    resource = 
      case_when(
        type == "hotline" |
          type == "legal_services" | 
          type == "hotline_and_legal_services" ~ "legal_services",
        type == "general_information" ~ "legal_general_info"
      )
  ) %>% 
  filter(!str_detect(county, "Orange|Los Angeles") | is.na(county))
```

eviction
```{r}
eviction_data <-
  read_sheet(
    legal_resource_key, 
    sheet = "Eviction resources", 
    skip = 1,
    col_types = "????c?cccc????cD??"
  ) %>% 
  mutate(
    type = type %>% str_to_lower() %>% str_replace_all(" ", "_"),
    resource = 
      case_when(
        type == "hotline" |
          type == "legal_services" | 
          type == "hotline_and_legal_services" ~ "legal_services",
        type == "general_information" ~ "legal_general_info"
      )
  ) %>% 
  filter(!str_detect(county, "Orange|Los Angeles") | is.na(county))
```

Farmers market data
```{r}
farmers_market_data <-
  read_sheet(
    farmers_market_key, 
    sheet = "FM Finder Data",
    col_types = "ccccdccccdccccccccccdddddcdddddcccccddcccDc",
    skip = 1
  ) %>% 
    mutate(
    address = case_when(
      !is.na(street) & !is.na(street_number)
      ~ str_glue("{street_number} {street}"),
      TRUE ~ street
    ) %>% 
      as.character() %>% 
    if_else(
      !is.na(cross_street_1), 
      str_glue("{.} & {cross_street_1}"), 
      .
    ) %>% 
      if_else(
        is.na(street) & !is.na(cross_street_1), 
        str_glue("{cross_street_1} & {cross_street_2}"), 
        .
      ) %>% 
      as.character(),
    notes = 
      if_else(!is.na(location), str_glue("Located at: {location}. "), "") %>% 
      as.character() %>% 
      if_else(
        offers_market_match == 1, 
        str_glue("{.}Offers market match ({market_match_level}) with maximum: {market_match_maximum}"),
        .
      ) %>% 
      as.character(),
    farmers_market = 1,
    county = str_to_lower(county) %>% str_replace(., " ", "_"),
    SNAP = if_else(offers_SNAP == 1, 1, 0),
    WIC = if_else(offers_wic_senior_fmnp == 1 | offers_wic_fvc == 1, 1, 0),
    days = days %>% replace_na(""),
    frequency = frequency %>% replace_na("")
    ) %>% 
  separate(
    senior_hours, into = c("senior_open_hour", "senior_close_hour"), sep = " - "
    ) %>% 
  mutate_at(
    vars(updated_time_open:senior_close_hour), 
    ~if_else(str_detect(., "0:00"), str_extract(., "(\\d{1,2}:\\d{1,2})"), 
             .
    ) %>% replace_na("0")
  )
```

output vars
```{r}
mega_map_variables <- 
  read_sheet(mega_map_key, sheet = "metadata") %>% 
  select(name = `Field Name`, type = `Value Type`)

output_variable_names <-
  mega_map_variables %>% 
  pull(name)
```

## creating output sheets to overwrite 
```{r}
resize <- function(df) {
  len <- size_of - 1
  for (i in 1:len) {
    df <- 
      df %>% 
      add_row()
  }
  df
}

generate_output_sheets <- function(data_set) {
  size_of <- count(data_set) %>% pull()
  mega_map_variables %>% 
    mutate(
      type =
        recode(
          type,
          text = '',
          combo = '',
          numeral = "0",
          date = as.character.Date(Sys.Date()) 
        )
    ) %>% 
    mutate(type = if_else(is.na(type), "0", type)) %>% 
    pivot_wider(names_from = name, values_from = type) %>% 
    mutate_if( ~ . == "0", as.double) %>% 
    resize() %>% 
    fill(everything())
}
```

# Various Processing Hour Functions

process hours_farmers_market 
```{r}
process_hours_farmers <- function(days, updated_time_open, updated_time_close, frequency, SENIOR = FALSE){
  days_col <- c("mon", "tues", "wed", "thr", "fri", "sat", "sun")
  days_col_senior <- c("sp_mon", "sp_tues", "sp_wed", "sp_thr", "sp_fri", "sp_sat", "sp_sun")
  days_long <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
  out <- rep("0", 7)
  names(out) <- days_col 
  out <- out %>% as_tibble_row() 
  
  if (str_detect(updated_time_open, ":")) {
  out <- out %>% 
    mutate(
      mon = if_else(str_detect(days, "Monday"), str_glue("{updated_time_open} - {updated_time_close}"), "0"),
      tues = if_else(str_detect(days, "Tuesday"), str_glue("{updated_time_open} - {updated_time_close}"), "0"),
      wed = if_else(str_detect(days, "Wednesday"), str_glue("{updated_time_open} - {updated_time_close}"), "0"),
      thr = if_else(str_detect(days, "Thursday"), str_glue("{updated_time_open} - {updated_time_close}"), "0"),
      fri = if_else(str_detect(days, "Friday"), str_glue("{updated_time_open} - {updated_time_close}"), "0"),
      sat = if_else(str_detect(days, "Saturday"), str_glue("{updated_time_open} - {updated_time_close}"), "0"),
      sun = if_else(str_detect(days, "Sunday"), str_glue("{updated_time_open} - {updated_time_close}"), "0")
    ) %>% 
    mutate_all(
      ., 
      ~as.character(.) %>% 
        if_else(
          str_detect(frequency,"\\w") & str_detect(., ":"), 
          str_c(frequency, ., sep = ": "), 
          .)
    )
  } else {
    out <- rep(updated_time_open, 7)
    names(out) <- days_col 
    out <- out %>%  as_tibble_row()
  }

  
  if (SENIOR == TRUE) {
    names(out) <- days_col_senior
    return(out)
  } else {
    return(out)
  }
  
}
```


process hours_legal 
```{r}
process_hours_legal <- function(day_hour, senior = FALSE) {
  
  days_long <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
  days_col_normal <- c("mon", "tues", "wed", "thr", "fri", "sat", "sun", "mon", "tues", "wed", "thr", "fri", "sat", "sun")
  days_col_senior <- str_c("sp_", days_col_normal)
  
  if (senior) {
    days_col <- days_col_senior
  } else {
    days_col <- days_col_normal
  }
  
  
  if (is.na(day_hour)) {
    out <- rep("0", 7)
    names(out) <- days_col[1:7]
    return(out %>% as_tibble_row())
  }
  
  try({
    out <- rep("0", 7)
    
    for (dt in str_split(day_hour, '[\\n;]+') %>% unlist()) {
      
      d <-  str_split(dt, ': ') %>% unlist() %>% .[1]
      t <- str_split(dt, ': ') %>% unlist() %>% .[2]
      
      # day range
      if (str_detect(d, '-')) {
        start = str_split(d, ' - ') %>% unlist() %>% .[1]
        end = str_split(d, ' - ') %>% unlist() %>% .[2]
        
        
        if (str_ends(start, 's')) {
          start <- str_sub(start, 1, -2)
        }
        if (str_ends(end, 's')) {
          end <- str_sub(end, 1, -2)
        }
        start_i = match(start, days_long)
        end_i = match(end, days_long[start_i : length(days_long)]) + start_i - 1
        
        for (i in seq(start_i, end_i)) {
          if (i > 7) {
            out[i %% 7] = t
          } else {
            out[i] = t
          }
        }
        # multiple, non contiguous days
      } else if (str_detect(d, ', ')) {
        for (single_d in str_split(d, ', ') %>% unlist()) {
          if (str_ends(single_d, 's')) {
            single_d <- str_sub(single_d, 1, -2)
          }
          start_i = match(single_d, days_long)
          out[start_i] = t
        }
        # single day
      } else {
        if (str_ends(d, 's')) {
          d <- str_sub(d, 1, -2)
        }
        start_i = match(d, days_long)
        
        if (is.na(start_i)) {
          stop()
        }
        out[start_i] = t
      }
    }
    
    out <- str_to_upper(out)
    names(out) <- days_col[1:7]
    return(out %>% as_tibble_row())
    
  }, silent = T)
  
  out <- rep(day_hour, 7)
  names(out) <- days_col[1:7]
  return(out %>% as_tibble_row())
  
}
```


```{r}
process_hours <- function(day_hour, senior = FALSE) {
  
  days_long <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
  days_col_normal <- c("mon", "tues", "wed", "thr", "fri", "sat", "sun", "mon", "tues", "wed", "thr", "fri", "sat", "sun")
  days_col_senior <- str_c("sp_", days_col_normal)
  
  if (senior) {
    days_col <- days_col_senior
  } else {
    days_col <- days_col_normal
  }
  
  
  if (is.na(day_hour)) {
    out <- rep("0", 7)
    names(out) <- days_col[1:7]
    return(out %>% as_tibble_row())
  }
  
  try({
    out <- rep("0", 7)
    
    for (dt in str_split(day_hour, '\\n') %>% unlist()) {
      
      d <-  str_split(dt, ': ') %>% unlist() %>% .[1]
      t <- str_split(dt, ': ') %>% unlist() %>% .[2]
      
      # day range
      if (str_detect(d, '-')) {
        start = str_split(d, ' - ') %>% unlist() %>% .[1]
        end = str_split(d, ' - ') %>% unlist() %>% .[2]
        
        
        if (str_ends(start, 's')) {
          start <- str_sub(start, 1, -2)
        }
        if (str_ends(end, 's')) {
          end <- str_sub(end, 1, -2)
        }
        start_i = match(start, days_long)
        end_i = match(end, days_long[start_i : length(days_long)]) + start_i - 1
        
        for (i in seq(start_i, end_i)) {
          if (i > 7) {
            out[i %% 7] = t
          } else {
            out[i] = t
          }
        }
        # multiple, non contiguous days
      } else if (str_detect(d, ', ')) {
        for (single_d in str_split(d, ', ') %>% unlist()) {
          if (str_ends(single_d, 's')) {
            single_d <- str_sub(single_d, 1, -2)
          }
          start_i = match(single_d, days_long)
          out[start_i] = t
        }
        # single day
      } else {
        if (str_ends(d, 's')) {
          d <- str_sub(d, 1, -2)
        }
        start_i = match(d, days_long)
        
        if (is.na(start_i)) {
          stop()
        }
        out[start_i] = t
      }
    }
    
    out <- str_to_upper(out)
    names(out) <- days_col[1:7]
    return(out %>% as_tibble_row())
    
  }, silent = T)
  
  out <- rep(day_hour, 7)
  names(out) <- days_col[1:7]
  return(out %>% as_tibble_row())
  
}
```

##process hours School Meals
```{r}
process_hours_SM <- function(day_of_week, open_hour, close_hour) {
  
  days_long <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
  days_col <- c("mon", "tues", "wed", "thr", "fri", "sat", "sun", "mon", "tues", "wed", "thr", "fri", "sat", "sun")
  
  
  if (is.na(day_of_week)) {
    out <- rep("0", 7)
    names(out) <- days_col[1:7]
    return(out %>% as_tibble_row())
  }
  
  else {
    out <- rep("0", 7)
    
    # for (d in days_of_week) {
    
    t = str_c(open_hour, " - ", close_hour)
    
    # day range
    # All weekdays
    if (str_detect(day_of_week, "Weekdays")) {
      
      for (i in seq(1, 5)) {
        out[i] = t
      }
      # multiple, non contiguous days
    } else if (str_detect(day_of_week, '-')) {
      start = str_split(day_of_week, ' - ') %>% unlist() %>% .[1]
      end = str_split(day_of_week, ' - ') %>% unlist() %>% .[2]
      
      
      if (str_ends(start, 's')) {
        start <- str_sub(start, 1, -2)
      }
      if (str_ends(end, 's')) {
        end <- str_sub(end, 1, -2)
      }
      start_i = match(start, days_long)
      end_i = match(end, days_long[start_i:length(days_long)]) + start_i - 1
      
      for (i in seq(start_i, end_i)) {
        if (i > 7) {
          out[i %% 7] = t
        } else {
          out[i] = t
        }
      }
      # multiple, non contiguous days
    } else if (str_detect(day_of_week, "through")) {
      
      start = str_split(day_of_week, ' through ') %>% unlist() %>% .[1]
      end = str_split(day_of_week, ' through ') %>% unlist() %>% .[2]
      
      
      if (str_ends(start, 's')) {
        start <- str_sub(start, 1, -2)
      }
      if (str_ends(end, 's')) {
        end <- str_sub(end, 1, -2)
      }
      start_i = match(start, days_long)
      end_i = match(end, days_long[start_i:length(days_long)]) + start_i - 1
      
      for (i in seq(start_i, end_i)) {
        if (i > 7) {
          out[i %% 7] = t
        } else {
          out[i] = t
        }
      }
      
    }
    
    else if (str_detect(day_of_week, ', ')) {
      for (single_d in str_split(day_of_week, ', ') %>% unlist()) {
        if (str_ends(single_d, 's')) {
          single_d <- str_sub(single_d, 1, -2)
        }
        start_i = match(single_d, days_long)
        out[start_i] = t
      }
      # single day
    } else {
      if (str_ends(day_of_week, 's')) {
        day_of_week <- str_sub(d, 1, -2)
      }
      start_i = match(day_of_week, days_long)
      
      if (is.na(start_i)) {
        stop()
      }
      out[start_i] = t
    }
    
    
    out <- str_to_upper(out)
    names(out) <- days_col[1:7]
    return(out %>% as_tibble_row())
    
  }
  
  out <- rep(days_of_week, 7)
  names(out) <- days_col[1:7]
  return(out %>% as_tibble_row())
  
}
```

##process hours Community resources
```{r}
process_hours_cr <- function(day_hour, senior = FALSE) {
  
  days_long <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
  days_col_normal <- c("mon", "tues", "wed", "thr", "fri", "sat", "sun", "mon", "tues", "wed", "thr", "fri", "sat", "sun")
  days_col_senior <- str_c("sp_", days_col_normal)
  
  if (senior) {
    days_col <- days_col_senior
  } else {
    days_col <- days_col_normal
  }
  
  
  if (is.na(day_hour)) {
    out <- rep("0", 8)
    names(out) <- c(days_col[1:7], "additional_hours")
    return(out %>% as_tibble_row())
  }
  
  try({
    out <- rep("0", 8)
    
    # split into groups of "days: hours"
    for (dt in str_split(day_hour, '[\\n;]+') %>% unlist()) {
      dt <- str_trim(dt)
      d <-  str_split(dt, ': ') %>% unlist() %>% .[1]
      t <- str_split(dt, ': ') %>% unlist() %>% .[2]
      
      # handles additional openings on odd days
      if (str_starts(str_trim(d, side = "left"), "\\d+")) {
        out[8] <- if (out[8] == "0") dt else str_c(out[8], dt, sep = ", ")
        next
      }
      
      # handles normal opening hours
      # day range
      if (str_detect(d, '-')) {
        start = str_split(d, ' - ') %>% unlist() %>% .[1]
        end = str_split(d, ' - ') %>% unlist() %>% .[2]
        
        # remove plurals
        if (str_ends(start, 's')) {
          start <- str_sub(start, 1, -2)
        }
        if (str_ends(end, 's')) {
          end <- str_sub(end, 1, -2)
        }
        
        # find corresponding day indeces
        start_i = match(start, days_long)
        end_i = match(end, days_long[start_i : length(days_long)]) + start_i - 1
        
        # populate output vector
        for (i in seq(start_i, end_i)) {
          if (i > 7) {
            out[i %% 7] = if (out[i %% 7] == "0") t else str_c(out[i %% 7], t, sep = ", ")
          } else {
            out[i] = if (out[i] == "0") t else str_c(out[i], t, sep = ", ")
          }
        }
        # multiple, non contiguous days
      } else if (str_detect(d, ', ')) {
        
        # split by days, find index and populate output
        for (single_d in str_split(d, ', ') %>% unlist()) {
          if (str_ends(single_d, 's')) {
            single_d <- str_sub(single_d, 1, -2)
          }
          start_i = match(single_d, days_long)
          out[start_i] = if (out[start_i] == "0") t else str_c(out[start_i], t, sep = ", ")
        }
        
        # single day
      } else {
        if (str_ends(d, 's')) {
          d <- str_sub(d, 1, -2)
        }
        start_i = match(d, days_long)
        
        if (is.na(start_i)) {
          stop()
        }
        out[start_i] = if (out[start_i] == "0") t else str_c(out[start_i], t, sep = ", ")
      }
    }
    
    out <- str_to_upper(out) %>% replace_na("")
    names(out) <- c(days_col[1:7], "additional_hours")
    return(out %>% as_tibble_row())
    
  }, silent = T)
  
  # handles unparsable text
  out <- c(rep(day_hour, 7), "0")
  names(out) <- c(days_col[1:7], "additional_hours")
  return(out %>% as_tibble_row())
}
```

##process hours SNAP
```{r}
process_hours_SNAP <- function(day_hour, senior = FALSE) {
  
  days_long <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
  days_col_normal <- c("mon", "tues", "wed", "thr", "fri", "sat", "sun", "mon", "tues", "wed", "thr", "fri", "sat", "sun")
  days_col_senior <- str_c("sp_", days_col_normal)
  
  if (senior) {
    days_col <- days_col_senior
  } else {
    days_col <- days_col_normal
  }
  
  
  if (is.na(day_hour)) {
    out <- rep("0", 7)
    names(out) <- days_col[1:7]
    return(out %>% as_tibble_row())
  }
  
  try({
    out <- rep("0", 7)
    
    for (dt in str_split(day_hour, '\\n') %>% unlist()) {
      
      d <-  str_split(dt, ': ') %>% unlist() %>% .[1]
      t <- str_split(dt, ': ') %>% unlist() %>% .[2]
      
      # day range
      if (str_detect(d, '-')) {
        start = str_split(d, ' - ') %>% unlist() %>% .[1]
        end = str_split(d, ' - ') %>% unlist() %>% .[2]
        
        
        if (str_ends(start, 's')) {
          start <- str_sub(start, 1, -2)
        }
        if (str_ends(end, 's')) {
          end <- str_sub(end, 1, -2)
        }
        start_i = match(start, days_long)
        end_i = match(end, days_long[start_i : length(days_long)]) + start_i - 1
        
        for (i in seq(start_i, end_i)) {
          if (i > 7) {
            out[i %% 7] = t
          } else {
            out[i] = t
          }
        }
        # multiple, non contiguous days
      } else if (str_detect(d, ', ')) {
        for (single_d in str_split(d, ', ') %>% unlist()) {
          if (str_ends(single_d, 's')) {
            single_d <- str_sub(single_d, 1, -2)
          }
          start_i = match(single_d, days_long)
          out[start_i] = t
        }
        # single day
      } else {
        if (str_ends(d, 's')) {
          d <- str_sub(d, 1, -2)
        }
        start_i = match(d, days_long)
        
        if (is.na(start_i)) {
          stop()
        }
        out[start_i] = t
      }
    }
    
    out <- str_to_upper(out)
    names(out) <- days_col[1:7]
    return(out %>% as_tibble_row())
    
  }, silent = T)
  
  out <- rep(day_hour, 7)
  names(out) <- days_col[1:7]
  return(out %>% as_tibble_row())
}
```

### Matching Output Variables to Input Variables
```{r}

yes_no_recode <- 
  c(
    "Yes" = 1,
    "No" = 0,
    .default = NA
  )

status_recode <- 
  c(
    "Open" = 1,
    "Closed" = 0,
    .default = NA
  )


contains_variable <- function(current_name){
  quo_current_name <- enquo(current_name)
  output <- tibble(x = rep(0, size_of)) ###Figure this out 
  if (current_name %in% input_variable_names) {
    output %>% 
      transmute(!! quo_current_name := data_set[!! quo_current_name] %>% pull())
  }
}
```


# Transforming the Data

## Domestic Violence 
```{r}
size_of <- dom_violence_db %>% count() %>% pull()
input_variable_names <- dom_violence_db %>% names()
data_set <- dom_violence_db


add_senior_hours <- function(row) {
  days_col_senior <- c("sp_mon", "sp_tues", "sp_wed", "sp_thr", "sp_fri", "sp_sat", "sp_sun")
  out_sp <- rep("0", 7)
  names(out_sp) <- days_col_senior[1:7]
  return(out_sp %>% as_tibble_row())
}


other_temp <- map_dfr(.x = data_set$days_of_week, .f = add_senior_hours)

temp <-  
  map_dfc(output_variable_names, contains_variable) %>% 
  bind_cols(
    data_set$days_hours %>%
      map_dfr(process_hours_cr, senior = F)
  ) %>% 
  mutate(
    region = 
      str_to_lower(data_set$county) %>% 
      str_replace_all(' ', '_') %>% str_c(., '_county'),
    zip = str_extract(data_set$address, "94\\d+|95\\d+") %>% as.numeric(),
    address =
      str_remove(data_set$address,"CA") %>%
      str_remove("94\\d+|95\\d+") %>%
      str_remove_all(","),
    contact = 
      str_remove(data_set$phone, "(ext\\. \\d{3,6})") %>% 
      str_remove_all("[^\\d]") %>%
      str_replace(.,"(\\d{3})(\\d{3})(\\d{4})$","(\\1) \\2-\\3") %>% 
      paste(str_extract(data_set$phone, "(ext\\. \\d{3,6})")) %>% 
      str_remove_all("NA"),
    status = if_else(str_detect(data_set$days_hours, 'Open'), 1, 0),
    delivery = ifelse(data_set$address == "Delivery", 1, 0),
    last_update = data_set$date_verified,
    updated_by = data_set$verified_by,
    state = 'CA',
    hotline = data_set$telecommunication,
    resource = "domviolence"
  ) %>% 
  bind_cols(other_temp)

output_sheet <-
  generate_output_sheets(data_set) %>% 
  mutate(
    additional_hours = 0,
    additional_hours1 = 0
  ) %>% 
  select(-(temp %>% names())) %>% 
  bind_cols(temp)

output_sheet <-
  output_sheet %>% 
  mutate(
    free = recode(data_set$free, !!! yes_no_recode) %>% replace_na(1),
    call_in_advance = recode(data_set$call_in_advance, !!! yes_no_recode),
    status = recode(data_set$status, !!! status_recode) %>% replace_na(1),
    farmers_market = str_detect(data_set$type, 'farmers') %>%  as.integer(),
    public = 
      if_else(
        str_detect(data_set$eligibility, "Public") == TRUE | is.na(data_set$eligibility), 
        1, 
        0
      ),
    seniors = 
      if_else(str_detect(data_set$eligibility, "Seniors") == TRUE, 1, 0) %>% replace_na(0),
    children = if_else(str_detect(data_set$eligibility, "Children") == TRUE, 1, 0) %>% replace_na(0),
    homeless = if_else(str_detect(data_set$eligibility, "Homeless") == TRUE, 1, 0) %>% replace_na(0),
    clients = if_else(str_detect(data_set$eligibility, "Clients") == TRUE, 1, 0) %>% replace_na(0), 
    uninsured = if_else(str_detect(data_set$eligibility, "Uninsured") == TRUE, 1, 0) %>% replace_na(0),
    residents = if_else(str_detect(data_set$eligibility, "Residents") == TRUE, 1, 0) %>% replace_na(0),
    women = if_else(str_detect(data_set$eligibility, "Women|women") == TRUE, 1, 0) %>% replace_na(0),
    lat = data_set$lat,
    lon = 
      map_dbl(data_set$lon, function(x) {
        l <- x[[1]]
        if (is.null(l)) {
          return( NA_real_)
        } else {
          return(l)
        }
      }
      )
  )
dom_violence_output <- 
  output_sheet %>% 
  select(all_of(output_variable_names))
```


Farmers Markets Data
```{r}
size_of <- farmers_market_data %>% count() %>% pull()
input_variable_names <- farmers_market_data %>% names()
data_set <- farmers_market_data

temp <- map_dfc(output_variable_names, contains_variable) %>% 
  bind_cols(
    pmap_dfr(
      list(
        data_set$days, 
        data_set$updated_time_open, 
        data_set$updated_time_close, 
        data_set$frequency
      ), 
      process_hours_farmers
    )
  ) %>% 
  bind_cols(
    pmap_dfr(
      list(
        data_set$days, 
        data_set$senior_open_hour, 
        data_set$senior_close_hour, 
        data_set$frequency,
        TRUE
      ), 
      process_hours_farmers
    )
  )

output_sheet <-
  generate_output_sheets(data_set) %>% 
  select(-(temp %>% names())) %>% 
  bind_cols(temp) %>% 
  mutate(
    region = data_set$county,
    last_update = data_set$date_verified,
    state = 'CA',
    resource = "grocery",
    updated_by = data_set$verified_by,
    status = if_else(str_detect(status, "Open"), 1, 0) %>% replace_na(0)
  )

farmers_output <- output_sheet %>% select(all_of(output_variable_names)) %>% 
  mutate_at(vars(mon:sp_sun), ~if_else(str_detect(., "CLOSED|Closed|closed"), "0" , .))
```


## SNAP data 

```{r}
size_of <- SNAP_data %>% count() %>% pull()
input_variable_names <- SNAP_data %>% names()
data_set <- SNAP_data
temp <-  
  map_dfc(output_variable_names, contains_variable) %>% 
  bind_cols(
    data_set$days_hours %>%
      map_dfr(process_hours_SNAP, senior = F)
  ) %>% 
  bind_cols(
    bind_cols(
      data_set$senior_hours %>%
        map_dfr(process_hours_SNAP, senior = T)
    )
  ) %>% 
  mutate(
    region = 
      str_to_lower(data_set$county) %>% 
      str_replace_all(' ', '_') %>% str_c(., '_county'),
    contact = 
      str_remove(data_set$phone, "(ext\\. \\d{3,6})") %>% 
      str_remove_all("[^\\d]") %>%
      str_replace(.,"(\\d{3})(\\d{3})(\\d{4})$","(\\1) \\2-\\3") %>% 
      paste(str_extract(data_set$phone, "(ext\\. \\d{3,6})")) %>% 
      str_remove_all("NA") ,
    status = if_else(str_detect(data_set$status, 'closed|no'), 0, 1) %>% replace_na(1),
    delivery = ifelse(data_set$address == "Delivery", 1, 0),
    last_update = data_set$date_verified,
    updated_by = data_set$verified_by,
    state = 'CA'
  )
output_sheet <-
  generate_output_sheets(data_set) %>% 
  select(-(temp %>% names())) %>% 
  bind_cols(temp) 

output_sheet <-
  output_sheet %>% 
  mutate(
    free = 0,
    SNAP = str_detect(data_set$type, 'SNAP') %>%  as.integer(),
    WIC = str_detect(data_set$type, 'WIC') %>%  as.integer(),
    WIC_only_store = if_else(SNAP == 0 & WIC == 1, 1, 0),
    resource = case_when(
      str_detect(data_set$type, "retailer|store") ~ 'grocery',
      str_detect(data_set$type, "restaurant") ~ 'restaurant',
      str_detect(data_set$type, "farm") ~ 'grocery',
      TRUE ~ data_set$type
    ),
    farmers_market = str_detect(data_set$type, 'farmers') %>%  as.integer(),
    special_hours = (!is.na(data_set$senior_hours)) %>% as.numeric(),
    ebt_online = data_set$EBT_pay_online,
    ebt_phone = data_set$EBT_pay_phone,
    zip = data_set$zip,
    lat = data_set$lat,
    lon = 
      map_dbl(data_set$lon, function(x) {
        l <- x[[1]]
        if (is.null(l)) {
          return( NA_real_)
        } else {
          return(l)
        }
      }
      )
  )


SNAP_output <- output_sheet %>% select(all_of(output_variable_names)) %>% 
  mutate_at(vars(mon:sp_sun), ~if_else(str_detect(., "CLOSED|Closed|closed"), "0" , .))
```

## Eviction
```{r}
size_of <- eviction_data %>% count() %>% pull()
input_variable_names <- eviction_data %>% names()
data_set <- eviction_data

temp <-  
    map_dfc(output_variable_names, contains_variable) %>% 
    bind_cols(
      data_set$days_hours %>%
        map_dfr(process_hours_legal, senior = F)
    ) %>% 
    bind_cols(
      bind_cols(
        data_set$sp_days_hours %>%
          map_dfr(process_hours_legal, senior = T)
      )
    )

output_sheet <-
  generate_output_sheets(data_set) %>% 
  select(-(temp %>% names())) %>% 
  bind_cols(temp) %>% 
  mutate(
    state = 'CA',
    legal_housing = 1,
    eviction =  1,
    residents = 1,
    region = data_set$county,
    last_update = data_set$last_updated
  ) 

eviction_output <- 
  output_sheet %>% 
  select(all_of(output_variable_names)) %>% 
  mutate(region = region %>% str_to_lower() %>% str_replace_all(" ", "_"))
```


##LEGAL
```{r}
iterate_sets <- function(data_set, data_set_name) {
  size_of <- data_set %>% count() %>% pull()
  input_variable_names <- data_set %>% names()
  temp <-  
    map_dfc(output_variable_names, contains_variable) %>% 
    bind_cols(
      data_set$days_hours %>%
        map_dfr(process_hours_legal, senior = F)
    ) %>% 
    bind_cols(
      bind_cols(
        data_set$sp_days_hours %>%
          map_dfr(process_hours_legal, senior = T)
      )
    ) %>% 
    mutate(
      region = 
        str_to_lower(data_set$county) %>% 
        str_replace_all(' ', '_') %>% str_c(., '_county'),
      contact = 
        str_remove(data_set$phone, "(ext\\. \\d{3,6})") %>% 
        str_remove_all("[^\\d]") %>%
        str_replace(.,"(\\d{3})(\\d{3})(\\d{4})$","(\\1) \\2-\\3") %>% 
        paste(str_extract(data_set$phone, "(ext\\. \\d{3,6})")) %>% 
        str_remove_all("NA"),
      status = if_else(str_detect(data_set$days_hours, 'CLOSED'), 0, 1),
      delivery = ifelse(data_set$address == "Delivery", 1, 0),
      last_update = data_set$date_verified,
      updated_by = data_set$verified_by,
      state = 'CA',
      hotline = if_else(str_detect(data_set$type, "hotline"), 1, 0)
    )
  output_sheet <-
    generate_output_sheets(data_set) %>% 
    select(-(temp %>% names())) %>% 
    bind_cols(temp) 
  
  
  if (data_set_name == "legal_resource_data") {
    output_sheet <-
      output_sheet %>% 
      mutate(
        free = if_else(str_detect(data_set$free, "\\w"), 1, 0) %>% replace_na(0),
        legal_housing = 
          if_else(
            str_detect(data_set$legal_area, "Housing & Homelessness"), 1, 0
          ),
        legal_worker_protection = 
          if_else(
            str_detect(
              data_set$legal_area, "Employment & Worker Protections"
            ), 1, 0),
        legal_healthcare =
          if_else(
            str_detect(data_set$legal_area, "Healthcare"), 1, 0
          ),
        legal_immigration = 
          if_else(
            str_detect(data_set$legal_area, "Immigration"), 1, 0
          ),
        legal_criminal = 
          if_else(
            str_detect(data_set$legal_area, "Criminal"), 1, 0
          ),
        legal_domviolence = 
          if_else(
            str_detect(data_set$legal_area, "Domestic Violence"), 1, 0
          ),
        legal_contracts = 
          if_else(
            str_detect(data_set$legal_area, "Contracts"), 1, 0
          ),
        legal_protester_defense = 
          if_else(
            str_detect(
              data_set$legal_area, "Protester"
            ), 1, 0),
        public = if_else(str_detect(data_set$eligibility, "Public") == TRUE, 1, 0),
        seniors = if_else(str_detect(data_set$eligibility, "Elderly") == TRUE, 1, 0),
        homeless = if_else(str_detect(data_set$eligibility, "Homeless") == TRUE, 1, 0),
        uninsured = if_else(str_detect(data_set$eligibility, "Uninsured") == TRUE, 1, 0), 
        residents = if_else(str_detect(data_set$eligibility, "Residents") == TRUE, 1, 0),
        low_income = if_else(str_detect(data_set$eligibility, "Low income") == TRUE, 1, 0),
        clients = if_else(str_detect(data_set$eligibility, "Clients") == TRUE, 1, 0),
        women = if_else(str_detect(data_set$eligibility, "Women|Pregnant") == TRUE, 1, 0),
        children = if_else(str_detect(data_set$eligibility, "Emancipated youth|Children") == TRUE, 1, 0),
        call_in_advance = recode(data_set$call_in_advance, !!! yes_no_recode),
        delivery = 0,
        status = recode(data_set$status, !!! status_recode),
        clients = recode(data_set$clients, !!! yes_no_recode),
        in_person = recode(data_set$clients, !!! yes_no_recode),
        residents = recode(data_set$residents_only, !!! yes_no_recode),
        special_hours = special_hours %>% as.numeric(),
        last_update = data_set$date_verified
      )
  }
  output_sheet %>% 
    select(
      all_of(output_variable_names)
    )
}

size_of <- legal_resource_data %>% count() %>% pull()
input_variable_names <- legal_resource_data %>% names()
data_set <- legal_resource_data
legal_resource_output <-
  iterate_sets(legal_resource_data, "legal_resource_data") %>% 
  mutate(
    notes = if_else(str_detect(mon, "1st"), paste(notes, mon), notes) %>% str_remove_all("NA")
    ) %>% 
  mutate_at(vars(mon:sun), ~if_else(str_detect(., "1st"), "0", .))

```

##School meals 
```{r}
size_of <- school_meal_data %>% count() %>% pull()
input_variable_names <- school_meal_data %>% names()
data_set <- school_meal_data

add_senior_hours <- function(row) {
  days_col_senior <- c("sp_mon", "sp_tues", "sp_wed", "sp_thr", "sp_fri", "sp_sat", "sp_sun")
  out_sp <- rep("0", 7)
  names(out_sp) <- days_col_senior[1:7]
  return(out_sp %>% as_tibble_row())
}

other_temp <- map_dfr(.x = data_set$days_of_week, .f = add_senior_hours)


temp <-  
  map_dfc(output_variable_names, contains_variable) %>% 
  bind_cols(
    pmap_dfr(
      list(data_set$days_of_week, data_set$open_hour, data_set$close_hour),
      process_hours_SM
    )
  ) %>% 
  bind_cols(other_temp) %>% 
  mutate(
    region = 
      str_to_lower(data_set$county) %>% 
      str_replace_all(' ', '_') %>% str_c(., '_county'),
    contact = 
      str_remove(data_set$phone, "(ext\\. \\d{3,6})") %>% 
      str_remove_all("[^\\d]") %>%
      str_replace(.,"(\\d{3})(\\d{3})(\\d{4})$","(\\1) \\2-\\3") %>% 
      paste(str_extract(data_set$phone, "(ext\\. \\d{3,6})")) %>% 
      str_remove_all("NA"),
    delivery = ifelse(data_set$address == "Delivery", 1, 0),
    last_update = data_set$date_verified,
    updated_by = data_set$verified_by,
    state = 'CA'
  )
output_sheet <-
  generate_output_sheets(data_set) %>% 
  select(-(temp %>% names())) %>% 
  bind_cols(temp) %>% 
  mutate(
    resource = 'meal',
    free = 1,
    #status = if_else(str_detect(data_set$status, "Open"), "1", "0") %>% as.numeric(), 
    children = 1,
    #Adults = if_else(str_detect(data_set$notes, "Adults|adults"), 1, 0),
    #residents = 
      # if_else(
      #   data_set$eligible_ages == "any child 18 and younger|residents", 0, 1
      # ),
    zip = data_set$zip,
    lat = data_set$lat,
    lon = 
      map_dbl(data_set$lon, function(x) {
        l <- x[[1]]
        if (is.null(l)) {
          return( NA_real_)
        } else {
          return(l)
        }
      }
      ),
  )

school_meal_output <- 
  output_sheet %>% select(all_of(output_variable_names)) %>% 
  mutate_at(vars(mon:sp_sun), ~if_else(str_detect(., "00:00"), str_replace_all(., "00:00", "00"), .))
```

##Comm resources 
```{r}
size_of <- comm_resource_data %>% count() %>% pull()
input_variable_names <- comm_resource_data %>% names()
data_set <- comm_resource_data


other_temp <- map_dfr(.x = data_set$days_of_week, .f = add_senior_hours)

temp <-  
  map_dfc(output_variable_names, contains_variable) %>% 
  bind_cols(
    data_set$days_hours %>%
      map_dfr(process_hours_cr, senior = F)
  ) %>% 
  mutate(
    region = 
      str_to_lower(data_set$county) %>% 
      str_replace_all(' ', '_') %>% str_c(., '_county'),
    zip = str_extract(data_set$address, "94\\d+|95\\d+") %>% as.numeric(),
    address =
      str_remove(data_set$address,"CA") %>%
      str_remove("94\\d+|95\\d+") %>%
      str_remove_all(","),
    contact = 
      str_remove(data_set$phone, "(ext\\. \\d{3,6})") %>% 
      str_remove_all("[^\\d]") %>%
      str_replace(.,"(\\d{3})(\\d{3})(\\d{4})$","(\\1) \\2-\\3") %>% 
      paste(str_extract(data_set$phone, "(ext\\. \\d{3,6})")) %>% 
      str_remove_all("NA"),
    status = if_else(str_detect(data_set$days_hours, 'CLOSED'), 0, 1),
    delivery = ifelse(data_set$address == "Delivery", 1, 0),
    last_update = data_set$date_verified,
    updated_by = data_set$verified_by,
    state = 'CA',
    hotline = if_else(med_hotline == 1, 1, 0)
  ) %>% 
  bind_cols(other_temp)

output_sheet <-
  generate_output_sheets(data_set) %>% 
  mutate(
    additional_hours = 0,
    additional_hours1 = 0
  ) %>% 
  select(-(temp %>% names())) %>% 
  bind_cols(temp)

output_sheet <-
  output_sheet %>% 
  mutate(
    free = recode(data_set$free, !!! yes_no_recode) %>% replace_na(1),
    call_in_advance = recode(data_set$call_in_advance, !!! yes_no_recode),
    status = recode(data_set$status, !!! status_recode) %>% replace_na(1),
    farmers_market = str_detect(data_set$type, 'farmers') %>%  as.integer(),
    public = 
      if_else(
        str_detect(data_set$eligibility, "Public") == TRUE | is.na(data_set$eligibility), 
        1, 
        0
      ),
    seniors = 
      if_else(str_detect(data_set$eligibility, "Seniors") == TRUE, 1, 0) %>% replace_na(0),
    children = if_else(str_detect(data_set$eligibility, "Children") == TRUE, 1, 0) %>% replace_na(0),
    homeless = if_else(str_detect(data_set$eligibility, "Homeless") == TRUE, 1, 0) %>% replace_na(0),
    clients = if_else(str_detect(data_set$eligibility, "Clients") == TRUE, 1, 0) %>% replace_na(0), 
    uninsured = if_else(str_detect(data_set$eligibility, "Uninsured") == TRUE, 1, 0) %>% replace_na(0),
    residents = if_else(str_detect(data_set$eligibility, "Residents") == TRUE, 1, 0) %>% replace_na(0),
    women = if_else(str_detect(data_set$eligibility, "Women|women") == TRUE, 1, 0) %>% replace_na(0),
    notes = if_else(data_set$additional_hours == "0", 
                    data_set$notes, 
                    str_c(data_set$notes, 
                          " Additional hours: ", 
                          data_set$additional_hours)),
    lat = data_set$lat,
    lon = 
      map_dbl(data_set$lon, function(x) {
        l <- x[[1]]
        if (is.null(l)) {
          return( NA_real_)
        } else {
          return(l)
        }
      }
      )
  )
comm_resource_output <- 
  output_sheet %>% 
  select(all_of(output_variable_names))
```

## Black owned businesses
```{r}
size_of <- bob_db%>% count() %>% pull()
input_variable_names <- bob_db %>% names()
data_set <- bob_db

temp <- map_dfc(output_variable_names, contains_variable) %>% 
  bind_cols(
      map_dfr(data_set$days_hours, process_hours_SNAP)
  ) %>% 
  bind_cols( map_dfr(.x = data_set$days_hours, .f = add_senior_hours))

output_sheet <-
  generate_output_sheets(data_set) %>% 
  select(-(temp %>% names())) %>% 
  bind_cols(temp) %>% 
  mutate(
    state = 'CA',
    resource = "restaurant",
    bob = 1,
    provider_name = data_set$provider_name
  ) %>% 
  mutate_at(vars(mon:sun), ~str_replace_all(., "CLOSED", "0")) %>% 
  mutate(region = data_set$location %>% str_to_lower(.) %>% str_replace_all(., " " , "_"))


bob_output <- output_sheet %>% select(all_of(output_variable_names)) %>% mutate(last_update = as.Date(last_update, origin = "2020-07-07"))
```



## combining things 
```{r}
final_output <-
  bind_rows(
    SNAP_output, 
    #school_meal_output, 
    comm_resource_output,
    legal_resource_output, 
    farmers_output,
    bob_output,
    eviction_output,
    dom_violence_output
  ) %>% 
  filter(!is.na(provider_name) | !is.na(provider_addloc)) %>% 
  mutate(
    alameda = if_else(str_detect(region,"alameda"), 1, 0),
    santa_clara = if_else(str_detect(region,"santa_clara"), 1, 0),
    contra_costa = if_else(str_detect(region,"contra_costa"), 1, 0),
    monterey = if_else(str_detect(region, "monterey"), 1, 0),
    marin = if_else(str_detect(region,"marin"), 1, 0),
    san_mateo = if_else(str_detect(region, "san_mateo"), 1, 0),
    sonoma = if_else(str_detect(region,"sonoma"), 1, 0),
    solano = if_else(str_detect(region,"solano"), 1, 0),
    napa = if_else(str_detect(region,"napa"), 1, 0),
    san_francisco = if_else(str_detect(region,"san_francisco"), 1, 0),
    meal_student = if_else(resource == "meal" & children == 1, 1, 0),
    must_show_id = must_show_id %>% replace_na(0)
  ) %>% 
  mutate_at(vars(alameda:san_francisco), ~if_else(str_detect(region, "bay_area|nationwide|california|state"), 1, .)) %>% 
  mutate_at(vars(mon:sp_sun), ~if_else(. == "" | is.na(.), "0", .)  %>% str_to_lower())
```


## Variable Debug
```{r}
variable <- "last_update"
SNAP_output %>% select(!! variable) 
comm_resource_output %>% select(!! variable)
legal_resource_output %>% select(!! variable)
school_meal_output %>% select(!! variable)
farmers_output %>% select(!! variable)
bob_output %>% select(!! variable) 
eviction_output %>% select(!! variable) 
#mega_map_db %>% select(!! variable)

```

Writing to sheets
```{r}
##writing to debug
final_output %>% 
  write_sheet(ss = "1ANfnP8ghzEdj7Tr1X9CgU5chTrhZmbW9s0qudidMs0g", sheet = "compiled sheet")

##debug help
school_meal_output %>% 
  write_sheet(ss = "1ANfnP8ghzEdj7Tr1X9CgU5chTrhZmbW9s0qudidMs0g", sheet= "school meals")

##write to db
final_output %>% 
  write_sheet(ss = "1SOUonPM40Si4LrPoGrkUnujbmLBxCQe1SdxydH2dVI4", sheet = "compiled sheet")

SNAP_output %>% 
  write_sheet(ss = "1ANfnP8ghzEdj7Tr1X9CgU5chTrhZmbW9s0qudidMs0g", sheet = "SNAP")

```
## Debugging days hours
```{r}
day_debug <-
  final_output %>% 
  select(provider_name, resource, mon:sp_sun)
```

## Big Local News
```{r}
final_output %>%   
  write_csv("~/Desktop/BLN.csv")
```

